### 2017-05-13 paper/evaluation.tex
first par RQ7

To answer this research question, we conducted an experiment involving
the six parallel configurations from Section~\ref{sec:modes}, and we
randomly selected 10 subjects from the medium and long groups (\ie,
tests suites that ran in at least one minute) identified in
\numRQFeasibilityOne{}. \Jbc{Is this legit/acceptable/convincing?
$\rightarrow$}The rationale for this criteria was to maximize the
diversity of domains from the subjects, assuming these subjects have
test suites with different characteristics (\eg, architectural design
and rate of cpu/io-bound operations).
    The rationale for this selection criteria was to maximize the chances
    of observing speedup and flakiness, assuming that long-running tests
    also have many tests. Indeed, we confirmed that test suites in these
    projects contain at least 236 tests ($1,662.7$ in average).
To compare flakiness and efficiency, we used the sequential execution
of each subject's test suite as the \emph{control group} (\ie,
baseline). Notice that with parallelism enabled, the number of failing
tests may vary on different runs due to the non-deterministic
scheduling of threads and processes.  For that reason, we re-executed
the experiment and computed the average speedup and flakiness on each
scenario. 

>>>>

To answer this research question, we ran ten different subjects
against all configurations described in Section~\ref{sec:modes} and
compared their running times and rate of test flakiness.  We selected
subjects from the medium and long groups listed in
Section~\ref{sec:rqA} and ran their longest test module for testing.
The rationale is to obtain a diverse set of subjects exposing a wide
range of running times (range observed 1.1m-8.2m) and number of test
cases (range observed 54-17,513).  The rationale for fixing the number
of subjects in ten was to be able to finish execution in reasonable
time.  We ran each project on each configuration with ten seeds and
reported averages of time and flakiness.  Overall, we need to reran
test suites 600 times, 60 times (10x6 configurations) on each project.

%% \Jbc{Is this
%%   legit/acceptable/convincing?  $\rightarrow$}The rationale for this
%% criteria was to maximize the diversity of domains from the subjects,
%% assuming these subjects have test suites with different
%% characteristics (\eg, architectural design and rate of cpu/io-bound
%% operations).

To compare flakiness and efficiency, we used the sequential execution
of each subject's test suite as the \emph{control group} (\ie,
baseline). Notice that with parallelism enabled, the number of failing
tests may vary on different runs due to the non-deterministic
scheduling of threads and processes.  For that reason, we re-executed
the experiment and computed the average speedup and flakiness on each
scenario.

\Comment{
    The rationale for this selection criteria was to maximize the chances
    of observing speedup and flakiness, assuming that long-running tests
    also have many tests. Indeed, we confirmed that test suites in these
    projects contain at least 236 tests ($1,662.7$ in average).
}
